BAN: Neuroanatomical Aligning in Auditory Recognition between Deep Neural Network and Human Brain

### 2023-06-05 visual/dorsal/latex/neuro/response/ResponseLetter.tex

\documentclass[12pt,journal,onecolumn]{IEEEtran}

% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor}
\usepackage{graphicx}
\usepackage[table,xcdraw]{xcolor}
\usepackage[TABBOTCAP]{subfigure}
\usepackage{bm}
\usepackage{upgreek} 
\usepackage{amsmath}
\usepackage{breqn}
\usepackage{color}
\usepackage{cite}
\usepackage[none]{hyphenat}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{caption2}
\usepackage{setspace}

\usepackage{tikz}
\newcommand*{\circled}[1]{\lower.7ex\hbox{\tikz\draw (0pt, 0pt)%
		circle (.4em) node {\makebox[1em][c]{\small #1}};}}

\linespread{1.5}

\begin{document}

\begin{center}
	\textbf{\LARGE Response to Comments} 
\end{center}
\vspace{8pt}

\noindent NEUCOM-Manuscript: NEUCOM-D-21-03628R1 \\

\noindent Title: BTN: Neuroanatomical Aligning between Visual Object Tracking in Deep Neural Network and Smooth Pursuit in Brain \\

\noindent Dear Editor and Reviewers:

\textcolor{blue}{
We want to thank you and the review team for the detailed comments on our submission, and for the opportunity to revise and reconsider the paper to NEUROCOMPUTING.  
Those comments are all valuable and very helpful for revising and improving our paper, as well as the important guiding significance to our researches. 
We have studied these comments carefully and have made correction to meet with your approval. 
The responds to the reviewer's comments are labeled in blue, 
and the main corrections in the paper are marked in red to facilitate your reading. 
}

\vspace{8pt}

\newpage

\textbf{To Reviewer \#1:}

\textcolor{blue}{Thanks for the comments for our paper, we have revised the manuscript according to your recommendations as follows:}

\textbf{Comment (1).} In this paper, The author raises a viewpoint that in the visual object tracking problem, humans present behavioral modes (eye movement) that differ from the bounding box of single object tracking. 
Therefore, the main purpose is to evaluate the behavioral output mode, not only the tracking performance. 
This part needs to adds more content to explain why the evaluation of the behavioral output mode is more important which means why we need to consider brain-like score. 
Because in visual object tracking problem, the problem is the accuracy of object tracking. 
The reason for considering the result of behavioral output mode is not adequate for the reviewer.
% 为什么用行为输出模式
% 更接近于人。使模型的输出更加接近于人的响应。

\textbf{Response:} \textcolor{blue}{Thank you for your valuable comment.
%Maybe we did not explain it clearly in the previous manuscript. 
In the revised version, we have reorganized the introduction of Brain-like Tracking Score, especially the behavioral metrics. 
The purpose of behavioral benchmarks it to compute the similarity between source (e.g., a DNN model) and target (e.g., human) behavioral responses. 
% 第二段
Even within the visual behavioral domain of core object recognition, there are many similar behavioral metrics.
They use the metric of image-by-image patterns of human behavior [1]. 
For core eye object tracking tasks, human exhibits behavioral patterns that differ from ground truth labels. 
For example, in pedestrians tracking, humans may pay more attention to the head or even the face, while the visual tracking task focuses on the body or even torso.
One consequence of this is that DNNs can achieve 100\% accuracy but will not gain a perfect behavioral and cortical similarity score.
Thus, we use both the behavioral response pattern metric and cortical metric, not an overall accuracy metric, and higher scores are obtained by DNNs that produce and predict the human patterns.
Finally, we have emphasized it in Section 5.1 as follows: 
}

% 5.1章 第一段
\textcolor{red}{
``The aim of behavioral metrics is to calculate the
similarity between the DNN outputs and the human behavioral outputs in a specific problem [9]. 
In the human eye object tracking, the subjects’s attention is a circle scope and related to human pupil.
Thus, the behavioral modes (the position of eye gaze and the size of pupil) is modeled as a circle and differs from the bounding box in visual object tracking. 
Meanwhile, the main purpose is to realize human-like intelligence, not only the tracking accuracy [36]; and BTN obtains better behavioral similarity and can predict the position and scope of eye gaze well. 
Otherwise, the result is that DNNs gain perfect bounding box fitting but can not obtain a good eye gaze prediction performance. "
} \\
% APA：名字全部列出来，没有省略
%\textcolor{blue}{
%	[1] Schrimpf, M., Kubilius, J., Lee, M. J., Murty, N. A. R., Ajemian, R., \& DiCarlo, J. J. (2020). Integrative benchmarking to advance neurally mechanistic models of human intelligence. Neuron.
%} \\
\textcolor{blue}{
	[1] Rajalingham, R., Issa, E. B., Bashivan, P., Kar, K., Schmidt, K., \& DiCarlo, J. J. (2018). Large-scale, high-resolution comparison of the core visual object recognition behavior of humans, monkeys, and state-of-the-art deep artificial neural networks. Journal of Neuroscience, 38(33), 7255-7269.
} \\

%\begin{figure}[H]
%	\centering 
%	\includegraphics[width=0.9\textwidth]{imgs/inconsistency.png}
%\end{figure}
%
%\begin{figure}[H]
%	\centering 
%	\includegraphics[width=0.9\textwidth]{imgs/framework.png}
%\end{figure}
%\vspace{8pt}

\textbf{(2).} The paper says that the BTS may vary when the BTN is retrained. 
So only the given trained BTN is optimal. 
Does it means that the application of BTN is very limited according to its training dataset. 
How to improve the BTN so it could applied to the most conditions.

% 更好的架构对泛化能力的影响大于特定数据集上学习到的特征（权重）
% 即使权重信息并不能在任务间很好地迁移，但是网络架构可以很好地被迁移。
% 最佳的 ImageNet 模型没有给出最佳的图像特征。在 ImageNet 上训练的 ResNet 模型的特征始终优于那些在 ImageNet 上取得更高准确率的网络。
% 优化过的超参数训练的 inception v4 模型
\textbf{Response:} \textcolor{blue}{Thank you for your comment. 
The old version elaborates unclearly in explaining the training of the BTN. 
In the revised manuscript, we have rewritten our description about the discussion to make it more understandable.
Since BTN is a transferable problem, architectures transfer well across tasks.
However, it cannot be precluded that the BTS may vary when using same network architectures and different training settings. 
It is useful to improve the transfer by retraining the DNN with optimized training configurations. 
Therefore, we believe that only the given trained BTN is optimal and not all types of network structure.
In the application of BTN, we can perform grid search to select the optimal training settings, such as learning rate and weight decay, based on a validation set.
We have emphasized it in Section 7.2 as follows:
}

% 7.2章 第二段
% 只是特定训练好的模型是效果最好的，而不是网络结构就行(重新训练就可能不是最好的了)
% 具体地应用中怎么训练模型（寻找最优的训练配置）
\textcolor{red}{
``Nevertheless, the independent training configuration may be the essential characteristic that trains the DNN [68]. In addition, an auxiliary task does not have a very large impact on the score but notably improves the transfer effect [68]. 
Because the BTN is a transferable problem, it cannot be precluded that the BTS may vary when using different training settings. 
They claim that it is useful to tremendously improve the transfer effect by retraining the DNN with optimized configurations [68].
Therefore, we believe that only the given trained
BTN is optimal and not all model of network architecture. 
Practically speaking, we can perform grid search to select the optimal training settings based on a validation set."
} \\

%\begin{figure}[H]
%	\centering 
%	\includegraphics[width=0.9\textwidth]{imgs/inconsistency.png}
%\end{figure}

\vspace{8pt}

\textbf{(3).} The paper has raised a brain-like tracking network model to solve object tracking problem. 
But it appears that it contributes most to establish a neuroscience-like model rather than solving the object tracking problem. 
So is it necessary to use brain-like model to solve the object tracking problem than just using DNN?
% 不是主要解决SOT的问题：可解释的问题
% DNN的必要性，为什么不用其他 类脑模型。（复杂场景）

\textbf{Response:} \textcolor{blue}{Thanks for your professional suggestions. 
The goal of our work is mainly to solve the interpretability problem of visual tracking model and implement a brain-like architecture with both high accuracy and excellent brain similarity. 
In the revised manuscript, we have analysed the motivation of our work and the reason for using the brain-like model in our introduction as follows:
}

% TODO
% 第1章 第1段
\textcolor{red}{
``Amazingly, in
trained deep neural networks (DNNs) used to classify images [2], the middle layer in DNNs can partially explain why the nerve cell in the middle layer of the visual cortex has specific activations to an image [3, 4, 5, 6, 7, 8]. 
Furthermore, these models also partly predict primate image classification behavior and evaluations [9, 10].
Excellent models of the brain provide extraordinary opportunities for brain-computer interfaces, and these methods can be utilized to produce the expected activations in the cortical pathway [11]." 
} \\
% 第1章 第2段
\textcolor{red}{
``To capture cortical processing even more strictly
in these models, continued architectural search on
traditional visual datasets alone no longer seems
to be a feasible solution. 
Even though the great tracking performance in deeper DNNs has truly increased [12, 13], it is hopeless to raise the brain-like score [9, 14]. 
In addition, at the beginning, only partial modules can be obviously mapped to corresponding regions of the visual pathway, and the relations between the small number of visual regions and the numerous and complex modules in GoogleNet [15] or Inception-v4 [16] are inconspicuous. 
Finally, the network with high accuracy in the visual task becomes increasingly deeper except for several brain-like architectures for image classification [17, 18]." 
} \\

%\begin{figure}[H]
%	\centering 
%	\includegraphics[width=0.9\textwidth]{imgs/online_tracking.png}
%\end{figure}
%\vspace{8pt}

\textbf{(4).} Another suggestion is that it will be better to introduce the structure of the paper in the introduction part.
This paper has very good potential. 
The reviewer believes it could be an outstanding paper after revision.

\textbf{Response:} \textcolor{blue}{Thanks for your valuable suggestions.
In the revised manuscript, we have introduced the structure of the paper in the tail of our introduction part as follows:
}

% 第1章 第3段
\textcolor{red}{
``To address the interpretability problem of visual tracking model, in this study, we propose that aligning DNNs to anatomy will result in shallower, more interpretable, and more brain-like tracking models, named brain-like tracking network (BTN). 
The BTN is a shallow recurrent brain-like architecture of the brain pathway; hence, it has a much more brain-like structure. In section 4, we introduce the method utilized to analyse human behavioral and cortical data during object tracking. In section 5, we build a fancy measurement method for predicting eye movement behavior and neural activations on the brain-like tracking score (BTS).
In our experiments, we introduce a new benchmark dataset composed of behavioral and cortical recordings, and present an outstanding tracking result of 36.5\% at evaluating the model similarity of the visual pathway while obtaining a good tracking effect in the Tracking-Gump dataset [19]. 
We find that these results are mainly due to the brain-like architecture, in accordance with prior knowledge of the human cortical pathway processing stimuli input [17, 20, 18]. 
Finally, to compare the model activations between the RNN MT/MST in the BTN and the responses in the human middle temporal and medial superior temporal areas (MT/MST), we discover that the BTN predicts these cortical activations well, and it is also the first visual tracking model to do so on the neural recordings." 
}

%\begin{figure}[H]
%	\centering 
%	\includegraphics[width=0.9\textwidth]{imgs/result_MOT_one_two_stage.png}
%\end{figure}
\vspace{8pt}

\vspace{8pt}

\newpage

\textbf{To Reviewer \#3:}

\textcolor{blue}{Thanks for the comments for our paper, we have revised the manuscript according to your recommendations as follows:}

\textbf{(1).}  The literature review is not thorough about the application and the contributions. 
To highlight the contributions, it suggests reorganizing the section of the related work. 
At least, for each contribution, it should be novel and meaningful according to a thorough literature review. 
In the literature analysis, it is recommended to read the following works and consider to discuss their similar application scenarios in the introduction and discussion, 
Improved recurrent neural network-based manipulator control with remote center of motion constraints: Experimental results; 
A teleoperation framework for mobile robots based on shared control.
% 重新组织introduction和realted work，突出重点，并引用文章。

\textbf{Response:}  \textcolor{blue}{Thank you for your kind suggestion.
The goal of our work is mainly to solve the interpretability problem of visual tracking model.
In the revised manuscript, we have reorganized the corresponding description of recurrent neural networks and related applications in the section of related work, and emphasized it as follows:} \\
% 2.1第二段
\textcolor{red}{
``To track a target, it seems to be very suitable to use recurrences and glimpses, but they have only been employed successfully in monochromatic videos with simple backgrounds [23]. 
Some [27] obtained prominent results through representations of the target detector that is the input of a recurrent neural network (RNN) [28].
However, it needs to process each full frame. 
A recent study [29] utilized an RNN cropping explicitly to build attention in humans. 
Our study is similar to [23, 30], and utilizes human attention which is implemented with a long short memory network (LSTM) to extract the movement features well in multiple frames. 
In addition, we seek to design a brain-like network that will gain a superior BTS and exceed the existing tracking models on the Tracking-Gump dataset [19]."
} \\
\textcolor{red}{
[28] Su, H., Hu, Y., Karimi, H. R., Knoll, A., Ferrigno, G., \& De Momi, E. (2020). Improved recurrent neural network-based manipulator control with remote center of motion constraints: Experimental results. Neural Networks, 131, 291-299.
} \\
\textcolor{red}{[30] 
Luo, J., Lin, Z., Li, Y., \& Yang, C. (2019). A teleoperation framework for mobile robots based on shared control. IEEE Robotics and Automation Letters, 5(2), 377-384.
} \\
\vspace{8pt}

\textbf{(2).} It is recommended to present in the first section so that it can highlight the specific scope of this article. 
The meaning of the assessment experiment should be highlighted.
% 指定文章的研究范围
% 强调评估实验的意义（作用），为什么这么设计实验

\textbf{Response:} \textcolor{blue}{Thank you very much for your helpful comment. 
In the new manuscript, we have first present in our introduction so that it can highlight the specific scope of this article as follows: \\
% 第一章第二段
\textcolor{red}{
``To capture cortical processing even more strictly in these models, continued architectural search on traditional visual datasets alone no longer seems to be a feasible solution. 
Even though the great tracking performance in deeper DNNs has truly increased [12, 13], it is hopeless to raise the brain-like score [9, 14]. 
In addition, at the beginning, only partial modules can be obviously mapped to corresponding regions of the visual pathway, and the relations between the small number of visual regions and the numerous and complex modules in GoogleNet [15] or Inception-v4 [16] are inconspicuous. 
Finally, the network with high accuracy in the
visual task becomes increasingly deeper except for
several brain-like architectures for image classification [17, 18]."
} \\
Second, we have highlighted the meaning of the assessment experiment in our introduction and Section 6.3 as follows: \\
% 第一张第三段We find that开始
\textcolor{red}{
``We find that these results are mainly due to the brain-like architecture, in accordance with prior knowledge of the human cortical pathway processing stimuli input [17, 20, 18]. 
Finally, to compare the model activations between the RNN MT/MST in the BTN and the responses in the human middle temporal and medial superior temporal areas (MT/MST), we discover that the BTN predicts these cortical activations well, and it is also the first visual tracking model to do so on the neural recordings."
} \\
% 6.3 章第一段
\textcolor{red}{
``We compared various experimental results to explain why the proposed BTN is a brain-like tracking model. 
It is easy to see that the model architecture and training procedure are slightly different from other implementations of the visual tracking model."
} \\
% 6.3.1 第一段
\textcolor{red}{
``We design a brain-like BTN that follows neuroanatomical aligning more closely than classic DNNs.
Besides, the BTN achieves good tracking performance as measured by the BTS on Tracking Gump dataset. 
Therefore, the BTN satisfies both neuroanatomical limitations in neuroscience and engineering requirements in computer vision."
} \\
% 6.3.2 第一段 前两句
\textcolor{red}{
``A feedforward neural network can not predict the trend of time series, and thus cannot capture a brain-like response of the tracking model [18, 17]. 
By using recurrent connections, the BTN is able to predict time-varying activation in the corresponding cortex."
} \\
% 6.3.3 第一段
\textcolor{red}{
``Although the tracking performance is truly improved in the later training when improving the cortical similarity, we select the epoch with maximum BTS."
} \\
}
\\

\vspace{8pt}

\textbf{(3).} Maybe it is better to discuss the possibility to improve the scope using deep learning to learn and control robot behavior in the introduction, for example, 
An Incremental Learning Framework for Human-like Redundancy Optimization of Anthropomorphic Manipulators; 
Trajectory Online Adaption Based on Human Motion Prediction for Teleoperation.

\textbf{Response:} \textcolor{blue}{Thank you very much for your valuable comment. 
In the revised version, we have improved the scope using deep learning to learn and deploy in related application in our introduction as follows:
} 
% 第1章第2段
\textcolor{red}{
``To capture cortical processing even more strictly in these models, continued architectural search on traditional visual datasets alone no longer seems to be a feasible solution. 
Even though the great tracking performance in deeper DNNs has truly increased [12, 13], it is hopeless to raise the brain-like score [9, 14]. 
In addition, at the beginning, only partial modules can be obviously mapped to corresponding regions of the visual pathway, and the relations between the small number of visual regions and the numerous and complex modules in GoogleNet [15] or Inception-v4 [16] are inconspicuous. 
Finally, the network with high accuracy in the visual task becomes increasingly deeper except for several brain-like architectures for image classification [17, 18]. "
} \\
\textcolor{red}{[13] Luo, J., Huang, D., Li, Y., \& Yang, C. (2021). Trajectory Online Adaption Based on Human Motion Prediction for Teleoperation. IEEE Transactions on Automation Science and Engineering.
} \\
\textcolor{red}{[14] Su, H., Qi, W., Hu, Y., Karimi, H. R., Ferrigno, G., \& De Momi, E. (2020). An incremental learning framework for human-like redundancy optimization of anthropomorphic manipulators. IEEE Transactions on Industrial Informatics.
} \\
\\
\vspace{8pt}

\textbf{(4).} Figure 5 is not clear and we would suggest adding more details and labels to make it clear.

\textbf{Response:} \textcolor{blue}{Thank you for your kind suggestion.
Maybe we did not explain it clearly in the previous manuscript. 
We have emphasized it in Figure 5 as follows:
}
\begin{figure}[H]
	\centering 
	\includegraphics[width=0.5\textwidth]{imgs/tracking.png}
\end{figure}
\vspace{8pt}

### 2023-06-05 visual/face/brain_like/latex/bfn.tex
init

%!TEX program = pdflatex 
% !BIB program = bibtex
%% bare_jrnl.tex
%% V1.4b
%% 2015/08/26
%% by Michael Shell
%% see http://www.michaelshell.org/
%% for current contact information.
%%
%% This is a skeleton file demonstrating the use of IEEEtran.cls
%% (requires IEEEtran.cls version 1.8b or later) with an IEEE
%% journal paper.
%%
%% Support sites:
%% http://www.michaelshell.org/tex/ieeetran/
%% http://www.ctan.org/pkg/ieeetran
%% and
%% http://www.ieee.org/

@@

\author{Haidong~Wang,~Jianhua~Zhang,~and Ke Nai,% <-this % stops a space
	\thanks{H. Wang and J. Zhang are with the School of Computer Science and Electronic Engineering of Hunan University, Key Laboratory for Embedded and Network Computing of Hunan Province, Changsha 410082, China (e-mail: wanghaidong@hutb.edu.cn; zhangjianhua@hutb.edu.cn;
		naike@hnu.edu.cn).}
	\thanks{M. Wen is with State Grid Hunan Electric Power Company Limited Economical \& Technical Research Institute, Hunan Key Laboratory of Energy Internet Supply-demand and Operation, Changsha 410000, China (e-mail: hnjyy1903wen@126.com).}
% % <-this % stops a space
}

@@

% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
\begin{abstract}
Inspired by neuroanatomy, deep neural networks (DNNs) have recently developed from shallow network to exceedingly deep structures, providing excellent auditory recognition performance.
However, conventional DNNs usually do not easily connect with brain areas on account of their excessive network depth and absent biological constraints, such as recurrent connections. 
We propose a brain-like auditory network (BAN) with four neuroanatomically mapped regions and recurrence, guided by the brain-like auditory score (BAS), 
a novel benchmark to measure the model similarity of the human auditory recognition pathway. 
In addition, we propose that the middle temporal and medial superior temporal (T2/T3) areas in the cerebral cortex are equivalent to the designed network structure on the basis of auditory perception pathway, 
and indicate that the metrics between the neuroanatomical similarity in cerebral cortex and auditory recognition of the DNN are compatible. 
Despite having excellent recognition performance on the Music genres dataset, the BAN has achieved a high BAS. 
In summary, this research builds a BAN, a brain-like and recurrent DNN, as the first model of the cortical pathway of auditory recognition.
\end{abstract}

% Note that keywords are not normally used for peerreview papers.
\begin{IEEEkeywords} 
Auditory Recognition, Deep Neural Network, Brain-like Model, Neuroanatomical Similarity. 
\end{IEEEkeywords}

@@

\begin{figure*}
	\centering
	\includegraphics[width=6.7in]{figs/introduction.pdf}
	\caption{
		\textbf{
		Collaborative design between a DNN and neuroanatomy with a BAS.} 
		Through the quantitative brain-like score, we refer to the human brain and utilize acquired knowledge to enlighten the design of the BAN. 
		The BAN includes four regions that are mapped into the primary auditory cortex (A1), the belt or peripheral area (Belt), parabelt cortex (PB) and the areas of middle and superior temporal cortex (T2/T3). 
		CONV\textsubscript{V1} is the classical convolutional layer and performs preprocessing to reduce the data size.
		The RNN\textsubscript{Belt} and RNN\textsubscript{PB} and RNN\textsubscript{T2/T3} is recurrent neural network, as depicted in Section~\ref{sec:cornet_s_def} for details.
		The the upper-right image corresponds to the auditory recognition activation and predicted generes labels in the brain-aligned models, 
		while lower-right image represents the cortical activation and human choice with the same stimulus in the far left,
		which demonstrates the relationship between computer prediction performance and brain auditory recognition response with the BAS, as depicted in Section~\ref{sec:experiments}.
	}
	\label{fig:introduction}
\end{figure*}

@@

% /data3/dong/data/brain/auditory/Music_Genre_Classification_Pytorch-master/report.pdf, 1. Music
% 一定要在路径中添加latex/bin/win32/bibtex.exe，否则参考文献为问号，且不会报错
\IEEEPARstart{H}{earing} is crucial for identifying sound for humans, it is particularly important because of its role in the understanding and production of music.
Genre classification is a task that aims to predict music genre using audio signal.
Music genres are a set of descriptive keywords that convey high-level information about a music clip (jazz, classical and rock .etc).
According to Tzanetakis and Cook~\cite{tzanetakis2002musical}, the genre of music is a categorical label created by humans to characterize musical works.
The genre of music is characterized by a common characteristic shared by members.
These characteristics are typically associated with musical instruments, rhythmic structures and harmonized content.
Automatic music genre classification can help or replace human users in the process and will be a valuable addition to the music information retrieval system.
According to Nam~\cite{nam2018deep}, music genre classification has a significant impact on auditory recognition and recommendation of music streaming services.
In the above mentioned musical classification and tagging task solving methodology, it is very important to make the computer aware of the pattern of music and identify them.
The characteristics of this traditional framework are critical to the design of pipeline through feature engineering and classifier production.

When humans distinguish music, it is important to tell machines the feature inside music, just they distinguish genres through the sound of musical instruments or through rhythm.
This is commonly called hand engineering using domain knowledge.
But as we move on to the era of deep learning after 2015, a variety of attempts and high performance begin to emerge.
The deep learning methodology leverages less domain knowledge and allows feature learning.
In general, the deep learning methodology builds pipeline through linear part, line transformation, nonlinear part activation function, and optional pooling operation.
As you pass through these layers, the model learns feature and enables end-to-end learning.

@@

To capture cortical processing even more strictly in these models, continued architectural search on traditional visual datasets alone no longer seems to be a feasible solution. 
Even though the great performance in deeper DNNs has truly increased~\cite{ILSVRC15,luo2021trajectory}, it is hopeless to raise the brain-like score~\cite{rajalingham2018large,su2020incremental}. 
In addition, at the beginning, only partial modules can be obviously mapped to corresponding regions of the visual pathway, 
and the relations between the small number of visual regions and the numerous and complex modules in GoogleNet~\cite{szegedy2015going} or Inception-v4~\cite{szegedy2017inception} are inconspicuous. 
Finally, the network with high accuracy in the visual task becomes increasingly deeper except for several brain-like architectures for image classification~\cite{TangSchrimpfLotter2018Recurrent, kar2019evidence}.

To address the interpretability problem of auditory recognition model, in this study, we propose that neuroanatomical aligning DNNs will result in more interpretable, more shallower, and more brain-like models, named brain-like auditory recognition network (BAN).
The BAN is a shallow recurrent brain-like architecture of the brain pathway; 
hence, it has a much more brain-like structure. 
In section \ref{sec:data_analysis}, we introduce a method utilized to analyse cortical data and human behavioral during auditory recognition. 
In section \ref{sec:bas}, we build a fancy measurement method for predicting auditory recognition behavior and neural activations on the brain-like auditory recognition score (BAS). 
In our experiments, we introduce a new benchmark dataset composed of behavioral and cortical recordings, 
and present an outstanding recognition result of at evaluating the model similarity of the auditory recognition pathway while obtaining a good prediction effect in the Music genres dataset~\cite{nakai2022music}. 
We find that these results are mainly due to the brain-like architecture, in accordance with prior knowledge of the human cortical pathway processing stimuli input~\cite{TangSchrimpfLotter2018Recurrent, yin2020deep, kar2019evidence}. 
Finally, to compare the model activations between the RNN\textsubscript{T2/T3} in the BAN and the responses in the human middle temporal and superior temporal areas (T2/T3), we discover that the BAN predicts these cortical activations well, 
and it is also the first auditory recognition model to do so on the neural recordings.

@@

% 音频识别相关的神经网络
\subsection{Deep neural network}\par
Many works have recently shown that salient objects are extracted by a series of foveal views~\cite{mnih2014recurrent,draw}.
The object extraction module in the BAN is implemented with a two-dimensional gaussian filter~\cite{RATM} that is neuroanatomically explainable.
Focusing on specific appearance representations may be as important as spatial attention. 
An approach with recurrence can adaptively change the filter of the convolution module, therefore changing it to presentations on a frame and optimizing model performance~\cite{stollenga2014deep}. 
The filters of the dynamic filter network (DFN)~\cite{brabandere2016dynamic} are obtained online based on the input feature, and the DFN implements model compression without degrading the accuracy. 
Input-dependent state transitions can help to learn the markovian decision model~\cite{karl2017deep}. 
We do not follow the results, and use the idea to predict the salient feature.

>>>>

%% bare_jrnl.tex
%% V1.4b
%% 2015/08/26
%% by Michael Shell
%% see http://www.michaelshell.org/
%% for current contact information.
%%
%% This is a skeleton file demonstrating the use of IEEEtran.cls
%% (requires IEEEtran.cls version 1.8b or later) with an IEEE
%% journal paper.
%%
%% Support sites:
%% http://www.michaelshell.org/tex/ieeetran/
%% http://www.ctan.org/pkg/ieeetran
%% and
%% http://www.ieee.org/

@@

\author{Haidong~Wang, Zhiyong Li, \emph{Member, IEEE},~Xuan He,~Ke Nai,~and Ming Wen% <-this % stops a space
	\thanks{H. Wang, Z. Li, K. Nai, S. Wang and J. Lv are with the School
		of Computer Science and Electronic Engineering of Hunan University, Key Laboratory for Embedded and Network Computing of Hunan Province, Changsha 410082,
		China (e-mail: haidong\_hnu@hnu.edu.cn; zhiyong.li@hnu.edu.cn;
		naike@hnu.edu.cn).}
	\thanks{M. Wen is with State Grid Hunan Electric Power Company Limited Economical \& Technical Research Institute, Hunan Key Laboratory of Energy Internet Supply-demand and Operation, Changsha 410000, China (e-mail: hnjyy1903wen@126.com).}
% % <-this % stops a space
}

@@

% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
\begin{abstract}
Inspired by neuroanatomy, deep neural networks (DNNs) have recently developed from shallow network structures to exceedingly deep structures, providing excellent recognition performance.
However, standard DNNs usually do not easily connect with brain areas on account of their excessive network depth and absent biological constraints, such as recurrent connections. 
We propose a brain-like auditory network (BAN) with four neuroanatomically mapped regions and recurrence, guided by the brain-like auditory score (BAS), 
a novel benchmark to measure the model similarity of the human smooth pursuit pathway. 
In addition, we propose that the middle temporal (MT) and medial superior temporal (MST) areas in the cerebral cortex are equivalent to the designed network structure on the basis of the continuous motion perception of the tracking pathway, 
and indicate that the metrics between the neuroanatomical similarity in the cerebral cortex and visual tracking of the DNN are compatible. 
Despite having significant tracking performance on the Tracking-Gump dataset, the BTN has achieved a high BTS. 
In summary, this research builds a BTN, a brain-like and recurrent DNN, as the first model of the cortical pathway of smooth pursuit.
\end{abstract}

% Note that keywords are not normally used for peerreview papers.
\begin{IEEEkeywords} 
Online Multi-object Tracking, End-to-end Model, Joint Detection and Data Association. 
\end{IEEEkeywords}

@@

\begin{figure*}
	\centering
	\includegraphics[width=6.7in]{figs/introduction.pdf}
	\caption{
		\textbf{
		Collaborative design between a DNN and neuroanatomy with a BAS.} 
		Through the quantitative brain-like score, we refer to the human brain and utilize acquired knowledge to enlighten the design of the BTN. 
		The BAN includes four regions that are mapped into the primary auditory cortex (A1), 		the belt or peripheral area, parabelt cortex (PB) and the areas of temporal cortex (T2/T3). 
		CONV\textsubscript{V1} is the classical convolutional layer and performs preprocessing to reduce the data size.
		The DFN\textsubscript{MT/MST} is dynamic filter network, and the RNN\textsubscript{FEF} is recurrent, as depicted in Section~\ref{sec:cornet_s_def} for details.
		The the upper-right image corresponds to the tracking activation and bounding box in the brain-aligned models, 
		while lower-right image represents the cortical activation and eye gaze position with the stimulus in the far left,
		which demonstrates the relationship between computer vision tracking performance and brain tracking response with the BTS, as depicted in Section~\ref{sec:experiments}.
	}
	\label{fig:introduction}
\end{figure*}

@@

% /data3/dong/data/brain/auditory/Music_Genre_Classification_Pytorch-master/report.pdf, 1. Music
\IEEEPARstart{M}{usic} genres are a set of descriptive keywords that convey high-level information about a music clip (jazz, classical and rock .etc).
Genre classification is a task that aims to predict music genre using audio signal.
According to Tzanetakis and Cook~\cite{tzanetakis2002musical}, the genre of music is a categorical label created by humans to characterize musical works.
The genre of music is characterized by a common characteristic shared by members.
These characteristics are typically associated with musical instruments, rhythmic structures and harmonized content.
Automatic music genre classification can help or replace human users in the process and will be a valuable addition to the music information retrieval system.
According to Nam~\cite{nam2018deep}, music genre classification has a significant impact on music search and recommendation of music streaming services.
In the above mentioned musical classification and tagging task solving methodology, it is very important to make the computer aware of the pattern of music and identify them.
The characteristics of this traditional framework are critical to the design of pipeline through feature engineering and classifier production.

When humans distinguish music, it is important to tell machines the feature inside the music, just they distinguish genres through the sound of musical instruments or through rhythm.
This is commonly called hand engineering using domain knowledge.
But as we move on to the era of deep learning after 2015, a variety of attempts and high performance begin to emerge.
The deep learning methodology leverages less domain knowledge and allows feature learning.
In general, the deep learning methodology builds pipeline through linear part, line transformation, nonlinear part activation function, and optional pooling operation.
As you pass through these layers, the model learns feature and enables end-to-end learning.

@@

To capture cortical processing even more strictly in these models, continued architectural search on traditional visual datasets alone no longer seems to be a feasible solution. 
Even though the great tracking performance in deeper DNNs has truly increased~\cite{ILSVRC15,luo2021trajectory}, it is hopeless to raise the brain-like score~\cite{rajalingham2018large,su2020incremental}. 
In addition, at the beginning, only partial modules can be obviously mapped to corresponding regions of the visual pathway, 
and the relations between the small number of visual regions and the numerous and complex modules in GoogleNet~\cite{szegedy2015going} or Inception-v4~\cite{szegedy2017inception} are inconspicuous. 
Finally, the network with high accuracy in the visual task becomes increasingly deeper except for several brain-like architectures for image classification~\cite{TangSchrimpfLotter2018Recurrent, kar2019evidence}.

To address the interpretability problem of visual tracking model, in this study, we propose that aligning DNNs to anatomy will result in shallower, more interpretable, and more brain-like tracking models, named brain-like tracking network (BTN).
The BTN is a shallow recurrent brain-like architecture of the brain pathway; 
hence, it has a much more brain-like structure. 
In section 4, we introduce the method utilized to analyse human behavioral and cortical data during object tracking. 
In section 5, we build a fancy measurement method for predicting eye movement behavior and neural activations on the brain-like tracking score (BTS). 
In our experiments, we introduce a new benchmark dataset composed of behavioral and cortical recordings, 
and present an outstanding tracking result of 36.5\% at evaluating the model similarity of the visual pathway while obtaining a good tracking effect in the Tracking-Gump dataset~\cite{gaze_forrest}. 
We find that these results are mainly due to the brain-like architecture, in accordance with prior knowledge of the human cortical pathway processing stimuli input~\cite{TangSchrimpfLotter2018Recurrent, yin2020deep, kar2019evidence}. 
Finally, to compare the model activations between the RNN\textsubscript{MT/MST} in the BTN and the responses in the human middle temporal and medial superior temporal areas (MT/MST), we discover that the BTN predicts these cortical activations well, 
and it is also the first visual tracking model to do so on the neural recordings.

@@

\subsection{Deep neural network}\par
Many works have recently shown that salient objects are extracted by a series of foveal views~\cite{mnih2014recurrent,draw}.
The object extraction module in the BTN is implemented with a two-dimensional gaussian filter~\cite{RATM} that is neuroanatomically explainable.
Focusing on specific appearance representations may be as important as spatial attention. 
An approach with recurrence can adaptively change the filter of the convolution module, therefore changing it to presentations on a frame and optimizing model performance~\cite{stollenga2014deep}. 
The filters of the dynamic filter network (DFN)~\cite{brabandere2016dynamic} are obtained online based on the input feature, and the DFN implements model compression without degrading the accuracy. 
Input-dependent state transitions can help to learn the markovian decision model~\cite{karl2017deep}. 
\textcolor{red}{
	We do not follow the results, and use the idea to predict the salient feature.}

\textcolor{red}{
	To track a target, it seems to be very suitable to use recurrences and glimpses, but they have only been employed successfully in monochromatic videos with simple backgrounds~\cite{RATM}. 
	Some~\cite{ning2017spatially} obtained prominent results through representations of the target detector that is the input of a recurrent neural network (RNN)~\cite{su2020improved}.
	However, it needs to process each full frame. 
	A recent study~\cite{gordon2017re3} utilized an RNN cropping explicitly to build attention in humans. 
	Our study is similar to~\cite{RATM,luo2019teleoperation}, and utilizes human attention which is implemented with a long short memory network (LSTM) to extract the movement features well in multiple frames. 
	In addition, we seek to design a brain-like network that will gain a superior BTS and exceed the existing tracking models on the Tracking-Gump dataset~\cite{gaze_forrest}.
}\par
